---
title: "PFL DATA REPORT"
format: 
  docx:
    reference-doc: 'C:/Users/bethany.kilpatrick/Boa Technology Inc/PFL Team - General/Testing Segments/Report_Template.docx'
editor: visual
editor_options: 
  chunk_output_type: console
execute: 
  error: true
  warning: false 
---

# CONFIDENTAL CONTENT FOR BOA EMPLOYEES ONLY. PLEASE CONTACT PFL DIRECTLY WITH ANY QUESTIONS.

+--------------------+------------------------------+
| ## Test Name       | ## Smith - Snow              |
|                    |                              |
| **Benefit:**       |                              |
+--------------------+------------------------------+
| **Date:**          | 3/2026                       |
+--------------------+------------------------------+
| **Test Type:**     | Performance                  |
+--------------------+------------------------------+
| **Configurations** | Baseline: Smith Stock        |
|                    |                              |
|                    | Test configuration: BOA FS 2 |
+--------------------+------------------------------+

# Hypotheses

-   H1: BOA FS2 systems will provide more even pressure distribution, with lower pressure points around the head.

# Methods

+---------------------------+---------------------------+
| **Equipment**             | **Measurements**          |
+===========================+===========================+
| -   Tactile Pressure head | Fit:                      |
|                           |                           |
|                           | -   Variation in pressure |
|                           |                           |
|                           | -   Peak pressures        |
|                           |                           |
|                           | -   Average pressures     |
|                           |                           |
|                           | -   Contact Area          |
+---------------------------+---------------------------+

## Configurations

| BOA FS1 | BOA FS2 |
|---------|---------|
|         |         |

# SUMMARY

Replace this text in final doc with takehome points from the test.

-   Point 1

-   Point 2

**Development Recommendations:**

-   Recommendation 1

```{r}
#| echo: false
#| warning: false
#| include: false


library(readxl)
library(tidyverse)
library(tm)
library(SnowballC)
library(RColorBrewer)
library(readxl)
library(brms)
library(patchwork)
library(tidyr)
library(fmsb)
library(gt)
library(ggplot2)
library("ggpubr") 
library(flextable) # install.packages("flextable")



rm(list=ls())
```

```{r}
#| echo: false
#| include: false


#Load in Compiled Qualitative Sheet
# qualDat <- read_xlsx('C:\\Users\\bethany.kilpatrick\\BOA Technology Inc\\PFL Team - General\\Testing Segments\\Helmets\\SmithPressure_Smith\\Qual_SN_Smith.xlsx') 


# Load in compiled pressure data
pressDat <- read.csv('C:\\Users\\bethany.kilpatrick\\Boa Technology Inc\\PFL Team - General\\Testing Segments\\Helmets\\2026_Performance_GiantPressure_Giant\\CSV\\0_CompiledHelmetData.csv') 

# Change for helmet sport segment
# pressDat <- subset(pressDat, pressDat$Helmet == 'SN')



baseline <- 'Aero' # baseline configuration

otherConfigs <- c('Bike') # other configurations tested against base
allConfigs <- c(baseline, otherConfigs) 

# qualDat$Config <- factor(qualDat$Config, allConfigs)

pressDat <- as_tibble(pressDat) # creating the data frame
# pressDat$Config <- factor(pressDat$Config, allConfigs)


withinSubPlotAvg <- function(inputDF, colName, dir = 'lower', yLabel = NULL) {
  # Validate the `dir` input
  if(!dir %in% c('lower', 'higher')){
    stop("The 'dir' argument must be either 'lower' or 'higher'.")
  }
  # Calculate the overall mean and SD for each Config, removing NA values
  overallMean <- inputDF %>%
    group_by(Config) %>%
    summarize(
      overallMean = mean(!! sym(colName), na.rm = TRUE),
      sd = sd(!! sym(colName), na.rm = TRUE),
      .groups = 'drop'
    )

  # Plotting with ggplot2
  plot <- ggplot() +
    geom_bar(data = overallMean, mapping = aes(x = as.factor(Config), y = overallMean, fill = 'Overall Mean'),
             stat = 'identity', alpha = 0.85) +
    geom_errorbar(data = overallMean, mapping = aes(x = as.factor(Config), ymin = overallMean - sd, ymax = overallMean + sd),
                  width = 0.25, size = 0.8) +
    scale_fill_manual(values = c('Overall Mean' = '#003C4C')) +
    xlab('Configuration') +
    theme(text = element_text(size = 16), legend.title = element_blank())
  # Set y-axis label
  if (!is.null(yLabel)) {
    plot <- plot + ylab(yLabel)
  } else {
    plot <- plot + ylab(paste0(colName))
  }
  print(plot)
}

# 
# 
# extractVals <- function(dat, mod, configNames, baseConfig, var, dir) {
#   
#   Config = rep(NA, length(configNames))
#   ProbImp = matrix(0, length(configNames))
#   lowCI = matrix(0, length(configNames))
#   highCI = matrix(0, length(configNames))
#   
#   for (i in 1:length(configNames)) {
#     configName = configNames[i]
#     configColName <- paste('b_Config', configName, sep = "")
#     posterior <- posterior_samples(mod)
#     
#     if (dir == 'lower'){
#       prob <- sum(posterior[,configColName] < 0) / length(posterior[,configColName])
#       
#     } else if (dir == 'higher') {
#       prob <- sum(posterior[,configColName] > 0) / length(posterior[,configColName])
#     }
#     
#     ci <- posterior_interval(mod, prob = 0.80)
#     ciLow <- ci[configColName,1] 
#     ciHigh <- ci[configColName,2]
#     
#     # Changed: removed group_by(Order), now calculates SD and mean across all data
#     meanSD <- sd(dat[[var]], na.rm = TRUE)
#     mean   <- mean(dat[[var]], na.rm = TRUE)
# 
#     ci_LowPct <- meanSD*ciLow/mean*100
#     ci_HighPct <- meanSD*ciHigh/mean*100
#     
#     Config[i] = configName
#     ProbImp[i] = prob
#     lowCI[i] = ci_LowPct
#     highCI[i] = ci_HighPct
#   }
#   
#   ProbImp = round(ProbImp*100)
#   lowCI = round(lowCI, 1)
#   highCI = round(highCI,1)
#   output = cbind(Config, ProbImp, lowCI, highCI)
#   
#   colnames(output) = c('Config', 'Probability of Improvement', 'Low end of CI', 'High end of CI')
#   
#   sentences = rep(NA, nrow(output))
#   
#   for (i in 1:nrow(output)){
#     if (as.numeric(output[i,2]) >= 90){
#       sentences[i] <- paste0('We have meaningful confidence that ',output[i,1], ' outperformed ', baseConfig, ' (',output[i,2], '%)', '\n', '\t', '- Estimated difference: ',output[i,3],' to ',output[i,4],'%' )
#     } else if (as.numeric(output[i,2]) >= 80) {      
#       sentences[i] <- paste('We have moderate confidence that',output[i,1], 'outperformed', baseConfig, '(',output[i,2], '%)','\n', '\t', '- Estimated difference:',output[i,3],'to',output[i,4],'%')
#     } else if (as.numeric(output[i,2]) >= 70){
#       sentences[i] <- paste('We have minimal confidence that',output[i,1], 'outperformed', baseConfig, '(',output[i,2], '%)','\n', '\t', 'Estimated difference:',output[i,3],'to',output[i,4],'%')
#     } else if (as.numeric(output[i,2]) >= 30){
#       sentences[i] <- paste('There were inconsistent differences between',output[i,1],'and',baseConfig,'(',output[i,2],'%)','\n', '\t', 'Estimated difference:',output[i,3],'to',output[i,4],'%')
#     } else if (as.numeric(output[i,2]) >= 20){
#       sentences[i] <- paste('We have minimal confidence that',output[i,1],'performed worse than',baseConfig,'(',(100 - as.numeric(output[i,2])),'%)','\n', '\t', 'Estimated difference:',output[i,3],'to',output[i,4],'%')
#     } else if (as.numeric(output[i,2]) >= 10){
#       sentences[i] <- paste('We have moderate confidence that',output[i,1],'performed worse than',baseConfig,'(',(100 - as.numeric(output[i,2])),'%)','\n', '\t', 'Estimated difference:',output[i,3],'to',output[i,4],'%')
#     } else {
#       sentences[i] <- paste('We have meaningful confidence that',output[i,1],'performed worse than',baseConfig,'(',(100 - as.numeric(output[i,2])),'%)','\n', '\t', 'Estimated difference:',output[i,3],'to',output[i,4],'%')
#     }
#   }
#   
#   writeLines(sentences)
#   return(invisible(NULL))
# }
 


# 
# 
# withinQualPlotAvg <- function(inputDF, colName, dir = 'lower', yLabel = NULL) {
#   # Validate the `dir` input
#   if(!dir %in% c('lower', 'higher')){
#     stop("The 'dir' argument must be either 'lower' or 'higher'.")
#   }
#   # Calculate the mean for each Subject and Config, removing NA values
#   meanDat <- inputDF %>%
#     group_by(Subject, Config) %>%
#     summarize(mean = mean(!! sym(colName), na.rm = TRUE), .groups = 'drop')
#   # Determine the best configuration based on the direction
#   if (dir == 'lower'){
#     whichConfig <- meanDat %>%
#       group_by(Subject) %>%
#       reframe(BestConfig = Config[which.min(mean)])
#   } else if (dir == 'higher') {
#     whichConfig <- meanDat %>%
#       group_by(Subject) %>%
#       reframe(BestConfig = Config[which.max(mean)])
#   }
#   # Rename BestConfig to Config for merging
#   whichConfig <- whichConfig %>%
#     rename(Config = BestConfig)
#   # Merge the best configuration back to the mean data
#   mergedData <- merge(meanDat, whichConfig, by = c("Subject", "Config"))
#   # Calculate overall mean for each Config, removing NA values
#   overallMean <- meanDat %>%
#     group_by(Config) %>%
#     summarize(overallMean = mean(mean, na.rm = TRUE), .groups = 'drop')
#   # Plotting with ggplot2
#   plot <- ggplot() +
#     geom_point(data = meanDat, mapping = aes(x = as.factor(Config), y = mean, group = Subject, color = 'Subject Means'), size = 3, alpha = 0.5) +
#     geom_line(data = meanDat, mapping = aes(x = as.factor(Config), y = mean, group = Subject, color = 'Subject Means'), alpha = 0.5) +
#     geom_point(data = overallMean, mapping = aes(x = as.factor(Config), y = overallMean, color = 'Overall Mean'), size = 4, shape = 17) +
#     geom_line(data = overallMean, mapping = aes(x = as.factor(Config), y = overallMean, group = 1, color = 'Overall Mean'), linewidth = 1.5) +
#     scale_color_manual(values = c('Subject Means' = 'grey', 'Overall Mean' = '#003C4C')) +
#     xlab('Configuration') +
#     theme(text = element_text(size = 16), legend.title = element_blank())
#   # Set y-axis label
#   if (!is.null(yLabel)) {
#     plot <- plot + ylab(yLabel)
#   } else {
#     plot <- plot + ylab(paste0(colName))
#   }
#   print(plot)
# }
```

## Qualitative

```{r}
#| echo: false
#| layout-ncol: 2
#| tbl-column: page-right
#| fig-column: page-left
#| warning: false
#| fig-height: 7
#| fig-width: 4


# 
# qualDat %>%
#   pivot_longer(cols = OverallComfort:`Side Fit`,
#                names_to = "Location", values_to = "Rating") %>%
#   group_by(Location, Config) %>%
#   summarize(
#     avg = round(mean(Rating, na.rm = TRUE), digits = 1)
# 
#   ) %>%
#   gt()
# 
# #Defining the rating for the location
# #Density plots for fit ratings of shoe locations
# qualDat <- pivot_longer(qualDat, cols = `Back Fit`:`Side Fit`, names_to = 'Location', values_to = 'Rating')
# 
# 
# 
# 
# qualDat$Location <- factor(qualDat$Location, c('Back Fit', 'Front Fit', 'Side Fit'))
# 
# 
# 
# a <- withinQualPlotAvg(qualDat, colName = 'OverallComfort', dir = 'higher', yLabel = 'Overall Fit Rating')
# 
# b <- withinQualPlotAvg(qualDat, colName = 'OverallSecurity', dir = 'higher', yLabel = 'Overall Security Rating') 
# 
# 
# d <- withinQualPlotAvg(qualDat, colName = 'LongTermFit', dir = 'higher', yLabel = 'Long Term Fit Rating')
# 
# 
# c <- ggplot(qualDat, mapping = aes(x = Rating, fill = Config)) +
#   geom_histogram(position = 'dodge', binwidth = 1) + facet_wrap(~Location) + scale_fill_manual(values=c("#999999", "#00966C", "#ECE81A","#DC582A","#CAF0E4")) +
#   ylab('Responses') + theme(text=element_text(size=12)) + geom_vline(xintercept = 5)
# 
# 
# figs <- ggarrange(a, b, c, ncol = 1, nrow = 3)
# 
# 
# figs
```

## All Sides of Head

### Peak Pressure

```{r}
#| echo: false
#| warning: false
#| include: false



maxAll<- pressDat %>%
  group_by(Config) %>%
  mutate(z_score = scale(MaxPress_all))



```

```{r}
#| echo: false
#| warning: false
#| layout-ncol: 2


p <- withinSubPlotAvg(maxAll, colName = 'MaxPress_all', dir = 'lower','Peak Pressure (kPa) - All Sides')

maxAll%>%
  group_by(Config) %>%
  summarize(
    mean_L_all = round(mean(MaxPress_all, na.rm = TRUE), 2),
    sd_L_all   = round(sd(MaxPress_all, na.rm = TRUE), 1),
  ) %>%
  flextable() %>%
  set_header_labels(
    Config     = "Configuration",
    mean_L_all = "Mean",
    sd_L_all   = "SD"
  )
```

### Contact Area

```{r}
#| echo: false
#| warning: false
#| include: false


ctAll <- pressDat %>% 
  mutate(z_score = scale(avg_all_ContArea)) %>% 
  group_by(Config)


```

```{r}
#| echo: false
#| warning: false
#| layout-ncol: 2


 


p <- withinSubPlotAvg(ctAll, colName = 'avg_all_ContArea', dir = 'higher','Contact Area (sq. in.) - All Sides')



ctAll %>%
  group_by(Config) %>%
  summarize(
    mean_L_all = round(mean(avg_all_ContArea, na.rm = TRUE), 2),
    sd_L_all   = round(sd(avg_all_ContArea, na.rm = TRUE), 1),
  ) %>%
  flextable() %>%
  set_header_labels(
    Config     = "Configuration",
    mean_L_all = "Mean",
    sd_L_all   = "SD"
  )
```

## Forehead

### Peak Pressure

```{r}
#| echo: false
#| warning: false
#| include: false

foreMax <- pressDat %>% 
  mutate(z_score = scale(frontalMax)) %>% 
  group_by(Config)
```

```{r}
#| echo: false
#| warning: false
#| layout-ncol: 2



p <- withinSubPlotAvg(foreMax, colName = 'frontalMax', dir = 'higher','Peak Pressure (kPa) - Forehead')




foreMax %>%
  group_by(Config) %>%
  summarize(
    mean_L_all = round(mean(frontalMax, na.rm = TRUE), 2),
    sd_L_all   = round(sd(frontalMax, na.rm = TRUE), 1),
  ) %>%
   flextable() %>%
  set_header_labels(
    Config     = "Configuration",
    mean_L_all = "Mean",
    sd_L_all   = "SD"
  )
```

### Contact Area

```{r}
#| echo: false
#| warning: false
#| include: false



foreContArea <- pressDat %>% 
  mutate(z_score = scale(ContArea_Forehead)) %>% 
  group_by(Config) 



```

```{r}
#| echo: false
#| warning: false
#| layout-ncol: 2 



p <- withinSubPlotAvg(foreContArea, colName = 'ContArea_Forehead', dir = 'lower','Contact Area (sq. in.) - Forehead') 




foreContArea%>%
  group_by(Config) %>%
  summarize(
     mean_MaxPress = round(mean(ContArea_Forehead, na.rm = TRUE), 2),
    sd_MaxPress   = round(sd(ContArea_Forehead, na.rm = TRUE), 1),
  ) %>%
   flextable() %>%
  set_header_labels(
    Config     = "Configuration",
    mean_MaxPress = "Mean",
    sd_MaxPress   = "SD"
  )
```

## Temporal

### Peak Pressures

```{r}
#| echo: false
#| warning: false
#| include: false



LpeakTMP<- pressDat %>%
  group_by(Config) %>%
  mutate(z_score = scale(MaxPress_L_Temporal))

```

```{r}
#| echo: false
#| warning: false
#| layout-ncol: 2 


p <- withinSubPlotAvg(LpeakTMP, colName = 'MaxPress_L_Temporal', dir = 'lower','Peak Pressure (kPa) - L Side')


LpeakTMP%>%
  group_by(Config) %>%
  summarize(
     mean_MaxPress = round(mean(MaxPress_L_Temporal, na.rm = TRUE), 2),
    sd_MaxPress   = round(sd(MaxPress_L_Temporal, na.rm = TRUE), 1),
  ) %>%
   flextable() %>%
  set_header_labels(
    Config     = "Configuration",
    mean_MaxPress = "Mean",
    sd_MaxPress   = "SD"
  )

```

### Contact Area

```{r}
#| echo: false
#| warning: false
#| include: false



L_contAreaTMP <- pressDat %>% 
  mutate(z_score = scale(ContArea_SideUpFrontL)) %>% 
  group_by(Config)

```

```{r}
#| echo: false
#| warning: false
#| layout-ncol: 2


p <- withinSubPlotAvg(L_contAreaTMP, colName = 'ContArea_SideUpFrontL', dir = 'higher','Contact Area (sq. in.) - L Temple to Parietal') 



L_contAreaTMP%>%
  group_by(Config) %>%
  summarize(
     mean_MaxPress = round(mean(ContArea_SideUpFrontL, na.rm = TRUE), 2),
    sd_MaxPress   = round(sd(ContArea_SideUpFrontL, na.rm = TRUE), 1),
  ) %>%
   flextable() %>%
  set_header_labels(
    Config     = "Configuration",
    mean_MaxPress= "Mean",
    sd_MaxPress   = "SD"
  )
```

## Posterior Parietal

### Peak Pressures

```{r}
#| echo: false
#| warning: false
#| include: false



LpeakDorOcc <- pressDat %>% 
  group_by(Config) %>%
  mutate(z_score = scale(MaxPress_L_Dorsal_Occipital))  
  
```

```{r}
#| echo: false
#| warning: false
#| layout-ncol: 2


p <- withinSubPlotAvg(LpeakDorOcc, colName = 'MaxPress_L_Dorsal_Occipital', dir = 'lower','Peak Pressure (kPa) - L Post. Parietal') 



LpeakDorOcc%>%
  group_by(Config) %>%
  summarize(
     mean_MaxPress = round(mean(MaxPress_L_Dorsal_Occipital, na.rm = TRUE), 2),
    sd_MaxPress   = round(sd(MaxPress_L_Dorsal_Occipital, na.rm = TRUE), 1),
  ) %>%
  flextable() %>%
  set_header_labels(
    Config     = "Configuration",
    mean_MaxPress = "Mean",
    sd_MaxPress   = "SD"
  )

```

### Contact Area

```{r}
#| echo: false
#| warning: false
#| include: false


PostPari_contArea<- pressDat %>% 
  mutate(z_score = scale(ContArea_SideUpRear)) %>% 
  group_by(Config)

```

```{r}
#| echo: false
#| warning: false
#| layout-ncol: 2


p <- withinSubPlotAvg(PostPari_contArea, colName = 'ContArea_SideUpRear', dir = 'higher','Contact Area (sq. in.) - Post. Parietal') 



PostPari_contArea %>%
  group_by(Config) %>%
  summarize(
     mean_MaxPress = round(mean(ContArea_SideUpRear, na.rm = TRUE), 2),
    sd_MaxPress   = round(sd(ContArea_SideUpRear, na.rm = TRUE), 1),
  ) %>%
  flextable() %>%
  set_header_labels(
    Config     = "Configuration",
    mean_MaxPress  = "Mean",
    sd_MaxPress   = "SD"
  )

```

## Occipital

### Peak Pressures

```{r}
#| echo: false
#| warning: false
#| include: false


LpeakDistOcc <- pressDat %>% 
  group_by(Config) %>%
  mutate(z_score = scale(MaxPress_L_Distal_Occipital))  
  
```

```{r}
#| echo: false
#| warning: false
#| layout-ncol: 2


p <- withinSubPlotAvg(LpeakDistOcc, colName = 'MaxPress_L_Distal_Occipital', dir = 'lower','Peak Pressure (kPa) - L Occipital') 

LpeakDistOcc %>%
  group_by(Config) %>%
  summarize(
     mean_MaxPress = round(mean(MaxPress_L_Distal_Occipital, na.rm = TRUE), 2),
    sd_MaxPress   = round(sd(MaxPress_L_Distal_Occipital, na.rm = TRUE), 1),
  ) %>%
  flextable() %>%
  set_header_labels(
    Config     = "Configuration",
    mean_MaxPress  = "Mean",
    sd_MaxPress  = "SD"
  )

```

### Contact Area

```{r}
#| echo: false
#| warning: false
#| include: false

Occ_ContArea <- pressDat %>% 
  mutate(z_score = scale(ContArea_SideLowRear)) %>% 
  group_by(Config)

```

```{r}
#| echo: false
#| warning: false
#| layout-ncol: 2



p <- withinSubPlotAvg(Occ_ContArea, colName = 'ContArea_SideLowRear', dir = 'higher','Contact Area (sq.in.) - Occipital')  



Occ_ContArea %>%
  group_by(Config) %>%
  summarize(
     mean_MaxPress = round(mean(ContArea_SideLowRear, na.rm = TRUE), 2),
    sd_MaxPress   = round(sd(ContArea_SideLowRear, na.rm = TRUE), 1),
  ) %>%
  flextable() %>%
  set_header_labels(
    Config     = "Configuration",
    mean_MaxPress = "Mean",
    sd_MaxPress   = "SD"
  )

```
